Looking for CDI Bias: WG Comprehension

### 2021-08-10 02-preliminary-WGcomp.Rmd
added ethnicity GLIMMER plot

First, let's get some wordbank data for American English. We'll start with production data from the CDI: Words & Gestures (WG) form.
We'll look for DIF based on 1) sex and 2) SES (high vs. low). 
Questions: How do we choose a dozen anchor items (that we expect to be unbiased)?

@@

```{r, echo=F}
load(here("data/eng_wg_rasch_group_models.Rds"))

@@

```{r, echo=F, fig.width=10, fig.height=5}
ggarrange(p1, p2)
```

>>>>

First, let's get some wordbank data for American English. We'll start with production data from the CDI: Words & Gestures (WG) form.
We'll look for DIF based on 1) sex, 2) SES (high vs. low), and 3) race/ethnicity. 
Questions: How do we choose a dozen anchor items (that we expect to be unbiased)?

@@

```{r, echo=F, include=F}
load(here("data/eng_wg_rasch_group_models.Rds"))

@@

```{r, echo=F, fig.width=10, fig.height=5, include=F}
ggarrange(p1, p2)
```

(See external PDFs and GLIMMER_WGcomp.R)
